---
title: "AFL Fantasy Ownership Comparison"
execute:
  echo: false
  warning: false
---

```{r}

library(arrow)
library(dplyr)
library(ggplot2)
library(plotly)
library(htmltools)
library(purrr)
library(reactable)
library(tidyr)
library(stringr)
library(scales)

```


# Top <span id="topn-page-heading">5</span> Players Comparison

## Filters

```{r}
player_data <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/2026/output/player_data.parquet") |> 
  mutate(
    id,
    label = paste0(first_name, " ", last_name, " || ", position, " || $", comma(price/1000), "K"),
    # Create position flags
    is_DEF = if_else(str_detect(position, "DEF"), 1, 0),
    is_MID = if_else(str_detect(position, "MID"), 1, 0),
    is_RUC = if_else(str_detect(position, "RUC"), 1, 0),
    is_FWD = if_else(str_detect(position, "FWD"), 1, 0)
  )

player_selections_plot <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/2026/output/player_selections_long.parquet") |> 
    mutate(
      direction = if_else(ownership_adjusted_diff>0, "Daily Increase", "Daily Decrease"),
      snapshot_label = "Snapshot"
    ) |> 
    left_join(player_data, by = "id") |> 
    mutate(
      snapshot_date = as.Date(snapshot_time, tz = "Australia/Sydney") - 1,
      full_name = paste(first_name, last_name)
    ) |> 
    arrange(desc(price))

# Get price range for defaults
max_price <- max(player_data$price, na.rm = TRUE)
min_price <- 0

```

```{r}
# Create filter controls
div(
  class = "filter-container",
  div(
    class = "filter-group",
    tags$label("Position:", style = "font-weight: bold; display: block; margin-bottom: 8px;"),
    div(
      class = "position-buttons",
      tags$button("All", id = "btn-all", class = "position-btn active", onclick = "togglePosition('all')"),
      tags$button("DEF", id = "btn-DEF", class = "position-btn", onclick = "togglePosition('DEF')"),
      tags$button("MID", id = "btn-MID", class = "position-btn", onclick = "togglePosition('MID')"),
      tags$button("RUC", id = "btn-RUC", class = "position-btn", onclick = "togglePosition('RUC')"),
      tags$button("FWD", id = "btn-FWD", class = "position-btn", onclick = "togglePosition('FWD')")
    )
  ),
  div(
    class = "filter-group",
    tags$label("Price Range:", style = "font-weight: bold; display: block; margin-bottom: 8px;"),
      div(
        class = "price-buttons",
        tags$button("All", id = "btn-price-all", class = "price-btn active", onclick = "togglePrice('all')"),
        tags$button("$230K - $350K", id = "btn-price-1", class = "price-btn", onclick = "togglePrice('230-350')"),
        tags$button("$351K - $660K", id = "btn-price-2", class = "price-btn", onclick = "togglePrice('351-660')"),
        tags$button("$661K - $830K", id = "btn-price-3", class = "price-btn", onclick = "togglePrice('661-830')"),
        tags$button("$831K - $1030K", id = "btn-price-4", class = "price-btn", onclick = "togglePrice('831-1030')"),
        tags$button("$1031K - $1250K", id = "btn-price-5", class = "price-btn", onclick = "togglePrice('1031-1250')")
        )
      ),
  div(
    class = "filter-group",
    tags$label("Number of Players:", style = "font-weight: bold; display: block; margin-bottom: 8px;"),
    tags$input(type = "number", id = "num-players", value = 5, min = 1, max = 10, step = 1, style = "width: 80px; padding: 6px; border: 1px solid #ced4da; border-radius: 4px;")
  ),
  div(
    style = "margin-top: 15px;",
    tags$button("Apply Filters", id = "apply-filters", class = "apply-btn", onclick = "applyFilters()")
  )
)
```

## Plot

```{r}
# Create initial plot with top 5 players by current ownership
top_5_initial <- player_selections_plot |>
  group_by(id) |>
  filter(snapshot_date == max(snapshot_date)) |>
  ungroup() |>
  arrange(desc(ownership_adjusted)) |>
  slice(1:5) |>
  pull(id)

gg_comparison <- player_selections_plot |>
  filter(id %in% top_5_initial) |>
  ggplot(aes(x = snapshot_date, y = ownership_adjusted, colour = full_name, group = full_name)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  xlab("Snapshot Date (End of Day)") +
  ylab("Owned by % (Adjusted)") +
  labs(title = "Top 5 Players by Adjusted Ownership") +
  scale_colour_discrete(name = "Player") +
  theme_minimal() +
  theme(
    legend.position = "right"
  )

p_comparison <- ggplotly(gg_comparison)

# Clean up legend labels
for(index in seq_along(p_comparison$x$data)) {
  original_name <- p_comparison$x$data[[index]]$name
  p_comparison$x$data[[index]]$name <- str_remove_all(original_name, "^\\(|,\\d+\\)$")
}

p_comparison$elementId <- "plotly_comparison"

p_comparison
```


## Table

::: {.panel-tabset}

### <span id="topn-tab-label">Top 5 Players</span>

```{r}
player_selections_table <- player_selections_plot |> 
  group_by(
    id, full_name, position, price, is_DEF, is_MID, is_RUC, is_FWD
  ) |> 
  mutate(
    days_ago = max(snapshot_date) - snapshot_date + 1
  ) |> 
  summarise(
    ownership_max = max(ownership),
    ownership_adjusted_max = max(ownership_adjusted),
    ownership_adjusted_which_max = which.max(ownership_adjusted),
    ownership_adjusted_max_date = snapshot_date[ownership_adjusted_which_max],
    ownership = tail(ownership, 1),
    ownership_adjusted_now = tail(ownership_adjusted, 1),
    change_yesterday = tail(ownership_adjusted_diff, 1),
    change_week = sum(tail(ownership_adjusted_diff, 7)),
    change_which_max = which.max(abs(tail(ownership_adjusted_diff, -1)))[1] + 1,
    change_max = ownership_adjusted_diff[change_which_max],
    change_max_date = snapshot_date[change_which_max],
    percent_change_yesterday =  last(ownership_adjusted) / nth(ownership_adjusted, -2) - 1,
    percent_change_week =  last(ownership_adjusted) / nth(ownership_adjusted, -7) - 1,
    gradient = mean(tail(ownership_adjusted_diff, -1)),
    .groups = "drop"
  ) |> 
  select(-change_which_max, -ownership_adjusted_which_max) |>
  relocate(ownership, ownership_adjusted_now, .after = "full_name") |> 
  arrange(desc(ownership_adjusted_now))

# Create a div that will be updated by JavaScript
div(id = "top5-table-container")

# Store the full table data as JSON for JavaScript to use
tags$script(HTML(paste0(
  "window.fullTableData = ", 
  jsonlite::toJSON(player_selections_table, dataframe = "rows"),
  ";"
)))
```

:::

## Explanation

This page shows the **Top <span id="topn-explainer">5</span> players** by adjusted ownership percentage that match your selected filters.

You can filter by:
- **Position**: Select one or more positions (DEF, MID, RUC, FWD). Players with dual positions (DPP) will appear if either position is selected.
- **Price Range**: Set minimum and maximum price thresholds.

The adjusted ownership percentage formula remains the same:

$$
(\text{Adjusted \% Ownership}) = \frac{(\text{\% Ownership}) } { (\text{Overall Team Completion \%}) }
$$

where:

$$
(\text{Overall Team Completion \%}) = \frac{ \sum ( \text{\% Ownership})}{  30 }
$$


```{=html}

<style>
.filter-container {
  background: #f8f9fa;
  padding: 20px;
  border-radius: 8px;
  margin-bottom: 20px;
  border: 1px solid #dee2e6;
}

.filter-group {
  margin-bottom: 15px;
}

.position-buttons {
  display: flex;
  gap: 10px;
  flex-wrap: wrap;
}

.position-btn {
  padding: 8px 16px;
  border: 2px solid #007bff;
  background: white;
  color: #007bff;
  border-radius: 4px;
  cursor: pointer;
  font-weight: 500;
  transition: all 0.2s;
}

.position-btn:hover {
  background: #e7f3ff;
}

.position-btn.active {
  background: #007bff;
  color: white;
}

.price-buttons {
  display: flex;
  gap: 10px;
  flex-wrap: wrap;
}

.price-btn {
  padding: 8px 16px;
  border: 2px solid #17a2b8;
  background: white;
  color: #17a2b8;
  border-radius: 4px;
  cursor: pointer;
  font-weight: 500;
  transition: all 0.2s;
}

.price-btn:hover {
  background: #e7f7f9;
}

.price-btn.active {
  background: #17a2b8;
  color: white;
}

.apply-btn {
  padding: 10px 24px;
  background: #28a745;
  color: white;
  border: none;
  border-radius: 4px;
  cursor: pointer;
  font-weight: 600;
  font-size: 14px;
  transition: all 0.2s;
}

.apply-btn:hover {
  background: #218838;
}

.price-inputs input {
  padding: 6px;
  border: 1px solid #ced4da;
  border-radius: 4px;
}
</style>

<script src="https://cdnjs.cloudflare.com/ajax/libs/reactable/0.4.4/reactable.min.js"></script>

<script>

// Store current filter state
let currentFilters = {
  positions: ['all'],
  priceRange: 'all',
  numPlayers: 5
};

// Toggle position filter
function togglePosition(position) {
  const btn = document.getElementById('btn-' + position);
  
  if (position === 'all') {
    // Deselect all other positions
    document.querySelectorAll('.position-btn').forEach(b => b.classList.remove('active'));
    btn.classList.add('active');
    currentFilters.positions = ['all'];
  } else {
    // Deselect "All" button
    document.getElementById('btn-all').classList.remove('active');
    
    // Toggle this position
    if (btn.classList.contains('active')) {
      btn.classList.remove('active');
      currentFilters.positions = currentFilters.positions.filter(p => p !== position);
    } else {
      btn.classList.add('active');
      currentFilters.positions.push(position);
    }
    
    // If no positions selected, select "All"
    if (currentFilters.positions.length === 0 || 
        (currentFilters.positions.length === 1 && currentFilters.positions[0] === 'all')) {
      document.getElementById('btn-all').classList.add('active');
      currentFilters.positions = ['all'];
    } else {
      // Remove 'all' if it's still in there
      currentFilters.positions = currentFilters.positions.filter(p => p !== 'all');
    }
  }
}

// Toggle price filter
function togglePrice(priceRange) {
  // Deselect all price buttons
  document.querySelectorAll('.price-btn').forEach(b => b.classList.remove('active'));
  
  // Activate the correct button based on priceRange value
  if (priceRange === 'all') {
    document.getElementById('btn-price-all').classList.add('active');
  } else if (priceRange === '230-350') {
    document.getElementById('btn-price-1').classList.add('active');
  } else if (priceRange === '351-660') {
    document.getElementById('btn-price-2').classList.add('active');
  } else if (priceRange === '661-830') {
    document.getElementById('btn-price-3').classList.add('active');
  } else if (priceRange === '831-1030') {
    document.getElementById('btn-price-4').classList.add('active');
  } else if (priceRange === '1031-1250') {
    document.getElementById('btn-price-5').classList.add('active');
  }
  
  currentFilters.priceRange = priceRange;
}

// Apply filters and update plot
function applyFilters() {
  // Get number of players
  const numPlayers = parseInt(document.getElementById('num-players').value) || 5;
  currentFilters.numPlayers = Math.min(Math.max(numPlayers, 1), 10); // Clamp between 1 and 10
  
  document.getElementById('topn-tab-label').textContent = `Top ${currentFilters.numPlayers} Players`;
  document.getElementById('topn-explainer').textContent = currentFilters.numPlayers;
  document.querySelectorAll('#topn-page-heading').forEach(el => {
    el.textContent = currentFilters.numPlayers;
  });
  
  // Parse price range
  let minPrice = 0;
  let maxPrice = Infinity;
  
  if (currentFilters.priceRange !== 'all') {
    const [min, max] = currentFilters.priceRange.split('-').map(p => parseFloat(p) * 1000);
    minPrice = min;
    maxPrice = max;
  }
  
  // Filter the data
  let filteredData = window.fullTableData.filter(player => {
    // Check price
    if (player.price < minPrice || player.price > maxPrice) {
      return false;
    }
    
    // Check position
    if (currentFilters.positions.includes('all')) {
      return true;
    }
    
    // Check if player matches any selected position
    for (let pos of currentFilters.positions) {
      if (pos === 'DEF' && player.is_DEF === 1) return true;
      if (pos === 'MID' && player.is_MID === 1) return true;
      if (pos === 'RUC' && player.is_RUC === 1) return true;
      if (pos === 'FWD' && player.is_FWD === 1) return true;
    }
    
    return false;
  });
  
  // Sort by current adjusted ownership and get top 5
   filteredData.sort((a, b) => b.ownership_adjusted_now - a.ownership_adjusted_now);
  const topN = filteredData.slice(0, currentFilters.numPlayers);
  
  // Get player IDs
  const topNIds = topN.map(p => p.id);
  
  // Update the plot
  updateComparisonPlot(topNIds);
  
  // Update the top N table
  updateTopNTable(topN);
}

// Update the comparison plot
function updateComparisonPlot(playerIds) {
  if (!playerIds || playerIds.length === 0) {
    return;
  }
  
  // Fetch data for all selected players
  const fetchPromises = playerIds.map(playerId => 
    fetch("json_data/af_adjusted_plot_data/" + playerId + ".json")
      .then(response => response.json())
  );
  
  Promise.all(fetchPromises).then(dataArray => {
    const traces = [];
    
    dataArray.forEach((data, index) => {
      const playerId = playerIds[index];
      const playerName = data.label[0].split('||')[0].trim();
      
      // Convert numeric dates to actual dates
      // Excel/R date origin is 1899-12-30, so we need to convert
      const convertToDate = (numericDate) => {
        const unixEpoch = new Date(1970, 0, 1); // January 1, 1970
        const millisPerDay = 24 * 60 * 60 * 1000;
        return new Date(unixEpoch.getTime() + numericDate * millisPerDay);
      };
      
      const dates = data.snapshot_x.map(convertToDate);
      
      // Create custom hover text
      const hoverText = dates.map((date, i) => {
        const dateStr = date.toLocaleDateString('en-AU', { 
          year: 'numeric', 
          month: 'short', 
          day: 'numeric' 
        });
        return `${playerName}<br>Date: ${dateStr}<br>Adjusted Ownership: ${data.snapshot_y[i].toFixed(2)}%`;
      });
      
      // Add line trace for this player
      traces.push({
        x: dates,
        y: data.snapshot_y,
        mode: 'lines+markers',
        name: playerName,
        type: 'scatter',
        line: { width: 3 },
        marker: { size: 6 },
        text: hoverText,
        hovertemplate: '%{text}<extra></extra>'
      });
    });
    
    let titleParts = [`Top ${currentFilters.numPlayers} Players`];

    // Add position filter to title
    if (!currentFilters.positions.includes('all')) {
      titleParts.push(`(${currentFilters.positions.join(', ')})`);
    }
    
    // Add price range to title
    if (currentFilters.priceRange !== 'all') {
      const priceStr = currentFilters.priceRange.replace('-', 'K - ');
      titleParts.push(`(${priceStr}K)`);
    }
    
    const layout = {
      title: titleParts.join(' ') + ' by Adjusted Ownership',
      xaxis: { title: 'Snapshot Date (End of Day)' },
      yaxis: { 
        title: 'Owned by % (Adjusted)',
        range: [0,100]
      },
      hovermode: 'closest',
      showlegend: true,
      legend: {
        title: { text: 'Legend' },
        orientation: 'v',
        x: 1.02,
        xanchor: 'left',
        y: 1,
        yanchor: 'top',
        font: { size: 10 }
      }
    };
    
    const config = {
      displayModeBar: true,
      displaylogo: false
    };
    
    Plotly.react('plotly_comparison', traces, layout, config);
    
  }).catch(error => {
    console.error('Error fetching comparison data:', error);
  });
}

// Update the Top 5 table
function updateTopNTable(topNData) {
  const tableHtml = `
    <table style="width: 100%; border-collapse: collapse; margin-top: 10px;">
      <thead>
        <tr style="background: #f8f9fa; border-bottom: 2px solid #dee2e6;">
          <th style="padding: 12px; text-align: left;">Player</th>
          <th style="padding: 12px; text-align: left;">Position</th>
          <th style="padding: 12px; text-align: right;">Price</th>
          <th style="padding: 12px; text-align: right;">Current Ownership</th>
          <th style="padding: 12px; text-align: right;">Change (Week)</th>
          <th style="padding: 12px; text-align: right;">% Change (Week)</th>
        </tr>
      </thead>
      <tbody>
        ${topNData.map((player, idx) => `
          <tr style="border-bottom: 1px solid #dee2e6; ${idx % 2 === 0 ? 'background: #f8f9fa;' : ''}">
            <td style="padding: 10px;">${player.full_name}</td>
            <td style="padding: 10px;">${player.position}</td>
            <td style="padding: 10px; text-align: right;">$${player.price.toLocaleString()}</td>
            <td style="padding: 10px; text-align: right;">${player.ownership_adjusted_now.toFixed(2)}%</td>
            <td style="padding: 10px; text-align: right; color: ${player.change_week >= 0 ? 'green' : 'red'};">
              ${player.change_week >= 0 ? '+' : ''}${player.change_week.toFixed(2)}%
            </td>
            <td style="padding: 10px; text-align: right; color: ${player.percent_change_week >= 0 ? 'green' : 'red'};">
              ${player.percent_change_week >= 0 ? '+' : ''}${(player.percent_change_week * 100).toFixed(2)}%
            </td>
          </tr>
        `).join('')}
      </tbody>
    </table>
  `;
  
  document.getElementById('top5-table-container').innerHTML = tableHtml;
}

// Initialize on page load
document.addEventListener('DOMContentLoaded', function() {
  // Apply initial filters to show default top 5
  applyFilters();
});

</script>

```
