---
title: "AFL Fantasy Top Coaches"
execute:
  echo: false
freeze: false
---

```{r}
#| message: false

library(modules)
library(arrow)
library(reactable)
library(dplyr)
library(purrr)
library(tidyr)
library(htmltools)

linked_icons <- use("../../modules/linked_icons.R")

content_creators_ranks <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/afl_fantasy/data/processed/content_creators_ranks.parquet") |> 
mutate(
    img_url = paste0("https://fantasy.afl.com.au/assets/media/avatars/afl/", user_id, ".png"),
    fantasy_url = if_else(is.na(team_id), NA_character_, paste0("https://fantasy.afl.com.au/classic/team/user/", team_id))
  ) |> 
  select("team_name", "rank_2022", "rank_2023", "rank_2024", "name", "individual_url", "organisation", "twitter", "facebook", "website", "YouTube", "spotify", "primary_url", "img_url", "fantasy_url", "user_id") |> 
  arrange(rank_2024)

overall_ranks_2024 <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/afl_fantasy/data/raw/2024/afl_fantasy_rankings.parquet")  |> 
  mutate(team_url = paste0("https://fantasy.afl.com.au/classic/team/user/", team_id)) |> 
  select(-team_id, -team_name, rank_2024 = rank)

overall_ranks_2023 <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/afl_fantasy/data/processed/overall_ranks_2023.parquet") |> 
  select(user_id, rank_2023 = rank)

overall_ranks_combined <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/afl_fantasy/data/processed/overall_ranks_combined_2022_2023.parquet") |> 
  left_join(overall_ranks_2024, by = "user_id") |> 
  mutate(
    img_url = paste0("https://fantasy.afl.com.au/assets/media/avatars/afl/", user_id, ".png"),
    fantasy_url = if_else(is.na(team_id), NA_character_, paste0("https://fantasy.afl.com.au/classic/team/user/", team_id)),
    is_content_creator = user_id %in% content_creators_ranks$user_id
  ) |> 
  select(team_name, is_content_creator, rank_2022, rank_2023, rank_2024, img_url, fantasy_url)


round_number <- max(overall_ranks_2024$round)

```


```{r}
reactable_b2b <- function(upper_bound) {
  ranks_data <- overall_ranks_combined |> 
    filter(rank_2022 <= upper_bound, rank_2023 <= upper_bound) |> 
    arrange(rank_2024)
  
  ranks_data |> 
    reactable(
      columns = list(
        team_name = colDef(
          name = "Fantasy Team",
          sticky = "left",
          cell = function(cell_value, row_index, column_name) {
            img_url <- ranks_data[["img_url"]][[row_index]]
            fantasy_url <- ranks_data[["fantasy_url"]][[row_index]]
            if(is.na(img_url)) {
              tags$div(
                tags$img(src = img_url, style = "height: 24px;width: 24px;"),
                " ",
                cell_value
              )
            } else{
              tags$a(
                tags$img(src = img_url, style = "height: 24px;width: 24px;"),
                " ",
                cell_value,
                href = fantasy_url, 
                target = "_blank"
                )              
            }
          },
          width = 200
        ),
        is_content_creator = colDef(
          name = "High Profile?", 
          cell = function(cell_value) {
            if(cell_value) "✅" else ""
          },
          width = 130
          ),
        rank_2022 = colDef(name = "2022", width = 75),
        rank_2023 = colDef(name = "2023", width = 75),
        rank_2024 = colDef(name = "2024", width = 75),
        img_url = colDef(show = FALSE),
        fantasy_url = colDef(show = FALSE)
      ),
      columnGroups = list(
        colGroup(name = "", columns = c("is_content_creator")),
        colGroup(name = "Overall Rank", columns = c("rank_2022", "rank_2023", "rank_2024"))
      ),
      fullWidth = FALSE,
      filterable = TRUE
    )
}
```


# {{< fa gauge-high >}} Overall Rank Pace

Not that the information below is as at the end of round `r round_number`.


```{r}
overall_ranks <- overall_ranks_2024 |> 
  left_join(overall_ranks_2023, by = "user_id")

rank_template <- tibble(
  rank = c(1, 100, 1000 * (1:9), 10000 *  (1:10))
)

top_teams_2023 <- rank_template |> 
  mutate(
    top_teams_2023 = map(rank, ~{
      overall_ranks |> 
        filter(rank_2023 <= .x) |> 
        summarise(
          returning_proportion = sum(!is.na(rank_2024))/.x,
          median_rank_2024 = round(median(rank_2024, na.rm = TRUE), 0),
          best_rank_2024 = round(min(rank_2024, na.rm = TRUE), 0),
          average_points_2024 = round(mean(points, na.rm = TRUE), 0)
        )
      })
  ) |> 
  unnest(top_teams_2023)

top_teams_2024 <- rank_template |> 
  mutate(
    top_teams_2024 = map(rank, ~{
      overall_ranks |> 
        filter(rank_2024 <= .x) |> 
        summarise(
          returning_proportion = sum(!is.na(rank_2023))/.x,
          points_yardstick = min(points, na.rm = TRUE)
        )
      })
  ) |> 
  unnest(top_teams_2024) |> 
  mutate(
    points_off_car = points_yardstick[1] - points_yardstick,
    points_off_hat = points_yardstick[2] - points_yardstick
  )


```


::: {.panel-tabset}


## 2024 Top Teams

```{r}
top_teams_2024 |> 
  reactable(
    columns = list(
      rank = colDef(name = "2024 Rank", format = colFormat(separators = TRUE)),
      returning_proportion = colDef(name = "Returning %", format = colFormat(percent = TRUE, digits = 1)),
    points_yardstick = colDef(name = "Yardstick", format = colFormat(separators = TRUE)),
    points_off_car = colDef(name = "Off Car", format = colFormat(separators = TRUE)),
    points_off_hat = colDef(name = "Off Hat", format = colFormat(separators = TRUE))
    ),
    columnGroups = list(
      colGroup(name = "Points", columns = c("points_yardstick", "points_off_car", "points_off_hat"))
    ),
    pagination = FALSE
  )
```

## 2023 Top Teams

```{r}
top_teams_2023 |> 
  reactable(
    columns = list(
      rank = colDef(name = "2023 Rank", format = colFormat(separators = TRUE)),
      returning_proportion = colDef(name = "Returning %", format = colFormat(percent = TRUE, digits = 1)),
    median_rank_2024 = colDef(name = "Median", format = colFormat(separators = TRUE)),
    best_rank_2024 = colDef(name = "Best", format = colFormat(separators = TRUE)),
    average_points_2024 = colDef(name = "Average Points (2024)", format = colFormat(separators = TRUE))
    ),
    columnGroups = list(
      colGroup(name = "2024 Rank", columns = c("median_rank_2024", "best_rank_2024"))
    ),
    pagination = FALSE
  )
```

:::

# {{< fa record-vinyl >}} Proven Track Record

These are the coaches that have ranked consistently highly in both 2022 and 2023.

::: {.panel-tabset}


## Top 100 🧢

The coaches listed below had back to back top 100 finishes (i.e. hats).

```{r}
reactable_b2b(100)
```


## Top 1000

The coaches listed below had back to back top 1000 finishes.

```{r}
reactable_b2b(1000)
```


## Top 2550

The coaches listed below had back to back top 2550 finishes.

::: darkModeOnly

Note that 2550 here is because this is the maximum ranks you can get from the AFL Fantasy APIs (i.e. $10 \times (2^{8}-1)$).

:::

```{r}
reactable_b2b(2550)
```

:::

Note that the repeat hat winners were shared in a tweet by the GOAT of Fantasy himself:

```{=html}
<blockquote class="twitter-tweet"><p lang="en" dir="ltr">By my count, there were 6 coaches who went back-to-back caps in <a href="https://twitter.com/hashtag/AFLFantasy?src=hash&amp;ref_src=twsrc%5Etfw">#AFLFantasy</a>:<br><br>Crayshaw<br>Dolmanators<br>JD - FTTV<br>MiniMonk<br>Mottram’s Marvel’s<br>Our Savior Laird<br><br>In this new age of high content, quality of coaches, forced trades and rolling lockouts, it’s a pretty amazing feat.</p>&mdash; Moreira’s Magic (@MoreirasMagic) <a href="https://twitter.com/MoreirasMagic/status/1697104930706972903?ref_src=twsrc%5Etfw">August 31, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
```




# {{< fa bullhorn >}} High Profile

Check out the track records of podcast hosts and other high profile coaches below.

Note that only data for the top 2550 is available for 2022 ranks.


```{r}
content_creators_ranks |> 
  select(-user_id) |> 
  reactable(
    columns = list(
      team_name = colDef(
        name = "Fantasy Team",
        sticky = "left",
        cell = function(cell_value, row_index, column_name) {
          img_url <- content_creators_ranks[["img_url"]][[row_index]]
          fantasy_url <- content_creators_ranks[["fantasy_url"]][[row_index]]
          if(is.na(img_url)) {
            tags$div(
              tags$img(src = img_url, style = "height:24px; width: 24px;"),
              " ",
              cell_value
              )
            } else{
              tags$a(
                tags$img(src = img_url, style = "height: 24px; width:24px;"),
                " ",
                cell_value,
                href = fantasy_url, 
                target = "_blank"
              )
            }
          },
        width = 175
      ),
      name = colDef(
        name = "Person",
        cell = function(cell_value, row_index, column_name) {
          individual_url <- content_creators_ranks[["individual_url"]][[row_index]]
          tags$a(
            cell_value,
            href = individual_url,
            target = "_blank"
            )
        },
        width = 175
      ),
      organisation = colDef(
        name = "Name",
        cell = function(cell_value, row_index, column_name) {
          primary_url <- content_creators_ranks[["primary_url"]][[row_index]]
          tags$a(
            cell_value,
            href = primary_url,
            target = "_blank"
            )
        },
        width = 200
      ),
      primary_url = colDef(
        name = "Links",
        cell = function(cell_value, row_index, column_name) {
          twitter <- content_creators_ranks[["twitter"]][[row_index]]
          facebook <- content_creators_ranks[["facebook"]][[row_index]]
          website <- content_creators_ranks[["website"]][[row_index]]
          YouTube <- content_creators_ranks[["YouTube"]][[row_index]]
          spotify <- content_creators_ranks[["spotify"]][[row_index]]
          
          tagList(
            if(isFALSE(twitter == "")) linked_icons$linked_twitter_icon(twitter) else NULL,
            if(isFALSE(facebook == "")) linked_icons$linked_facebook_icon(facebook) else NULL,
            if(isFALSE(website == "")) linked_icons$linked_globe_icon(website) else NULL,
            if(isFALSE(YouTube == "")) linked_icons$linked_youtube_icon(YouTube) else NULL,
            if(isFALSE(spotify == "")) linked_icons$linked_spotify_icon(spotify) else NULL
          )
        },
        width = 120
      ),
      rank_2022 = colDef(name = "2022", width = 75),
      rank_2023 = colDef(name = "2023", width = 75),
      rank_2024 = colDef(name = "2024", width = 75),
      individual_url = colDef(show = FALSE),
      twitter = colDef(show = FALSE),
      facebook = colDef(show = FALSE),
      website = colDef(show = FALSE),
      YouTube = colDef(show = FALSE),
      spotify = colDef(show = FALSE),
      img_url = colDef(show = FALSE),
      fantasy_url = colDef(show = FALSE)
    ),
    columnGroups = list(
      colGroup(name = "Overall Rank", columns = c("rank_2022", "rank_2023", "rank_2024")),
      colGroup(name = "", columns = c("name")),
      colGroup(name = "Organisation", columns = c("organisation", "twitter", "facebook", "website", "YouTube", "spotify", "primary_url"))
      ),
    fullWidth = FALSE,
    filterable = TRUE
  )


```

