---
title: "AFL Fantasy Projected Prices - Round 1"
execute:
  echo: false
  warning: false
---


```{r}

library(arrow)
library(dplyr)
library(reactable)
magic_number_r1 <- 10179.88
```

```{r}
r1_projected_price_changes <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/2026/output/r1_projected_price_changes.parquest")
price_format <- colFormat(separators = TRUE, suffix = "k")
```


# Disclaimer

> The below projections are an *early indication* only, actual price movements may deviate from below due to magic number being different from expected or subtle differences in AFL Fantasy pricing formula from what was applied below.

# R0 Hidden Prices

```{r}
r0_player_table <- r1_projected_price_changes |> 
  filter(
    played_r0
  ) |> 
  transmute(
    player_name,
    position,
    r0_score,
    starting_price = price / 1000,
    price_hidden = price_hidden / 1000,
    price_change_hidden = price_change_hidden / 1000,
    breakeven_hidden,
    r1_proj_change_r0 = r1_proj_change_r0 / 1000,
  ) |> 
  arrange(desc(r0_score))

r0_player_table |> 
  reactable(
    columns = list(
      player_name = colDef(name = "Player", sticky = "left"),
      position = colDef(name = "Position"),
      r0_score = colDef(name = "Round 0 Score"),
      starting_price = colDef(name = "Starting Price", format = price_format),
      price_hidden = colDef(name = "Hidden Price", format = price_format),
      price_change_hidden = colDef(name = "Hidden Change", format = price_format),
      breakeven_hidden = colDef(name = "Hidden Breakeven*"),
      r1_proj_change_r0 = colDef(name = "Proj. Price Change @ R0 Score**", format = price_format)
    ),
    filterable = TRUE,
    defaultPageSize = 10,
    pagination = TRUE,
  )

```


*: Breakeven to retain their hidden price
**: Projected price change if they repeat their R0 score


# Projected Price Changes

```{r}

price_change_table <- r1_projected_price_changes |> 
  arrange(desc(r1_proj_change_priced_at)) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
    across(starts_with("r1_proj_change_"), ~ .x/1000)
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    r1_proj_change_priced_at,
    starts_with("r1_proj_change_")
  ) |> 
  select(
    -r1_proj_change_r0
  )

price_change_table |> 
  reactable(
    columns = list(
      player_name = colDef(name = "Player", sticky = "left"),
      position = colDef(name = "Position"),
      played_r0 = colDef(name = "Played R0?"),
      starting_price = colDef(name = "Starting Price", format = price_format),
      priced_at_preseason = colDef(name = "Priced At"),
      r1_proj_change_priced_at = colDef(name = "@ Priced At", format = price_format),
      r1_proj_change_0 = colDef(name = "@ 0", format = price_format),
      r1_proj_change_10 = colDef(name = "@ 10", format = price_format),
      r1_proj_change_20 = colDef(name = "@ 20", format = price_format),
      r1_proj_change_30 = colDef(name = "@ 30", format = price_format),
      r1_proj_change_40 = colDef(name = "@ 40", format = price_format),
      r1_proj_change_50 = colDef(name = "@ 50", format = price_format),
      r1_proj_change_60 = colDef(name = "@ 60", format = price_format),
      r1_proj_change_70 = colDef(name = "@ 70", format = price_format),
      r1_proj_change_80 = colDef(name = "@ 80", format = price_format),
      r1_proj_change_90 = colDef(name = "@ 90", format = price_format),
      r1_proj_change_100 = colDef(name = "@ 100", format = price_format),
      r1_proj_change_110 = colDef(name = "@ 110", format = price_format),
      r1_proj_change_120 = colDef(name = "@ 120", format = price_format),
      r1_proj_change_130 = colDef(name = "@ 130", format = price_format),
      r1_proj_change_140 = colDef(name = "@ 140", format = price_format),
      r1_proj_change_150 = colDef(name = "@ 150", format = price_format)
    ),
    columnGroups = list(
        colGroup(name = "R1 projected price change, if R1 score is ...", columns = c("r1_proj_change_priced_at", "r1_proj_change_0", "r1_proj_change_10", "r1_proj_change_20", "r1_proj_change_30", "r1_proj_change_40", "r1_proj_change_50", "r1_proj_change_60", "r1_proj_change_70", "r1_proj_change_80", "r1_proj_change_90", "r1_proj_change_100", "r1_proj_change_110", "r1_proj_change_120", "r1_proj_change_130", "r1_proj_change_140", "r1_proj_change_150")),
        colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason"))
        ),
    filterable = TRUE,
    defaultPageSize = 10,
    pagination = TRUE
  )

```



# Projected Breakevens


```{r}
breakeven_table <- r1_projected_price_changes |> 
  arrange(r1_proj_breakeven_0) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    starts_with("r1_proj_breakeven_")
  )

breakeven_table |> 
  reactable(
    columns = list(
      player_name = colDef(name = "Player", sticky = "left"),
      position = colDef(name = "Position"),
      played_r0 = colDef(name = "Played R0?"),
      starting_price = colDef(name = "Starting Price", format = price_format),
      priced_at_preseason = colDef(name = "Priced At"),
      r1_proj_breakeven_neg150 = colDef(name = "-150k"),
      r1_proj_breakeven_neg125 = colDef(name = "-125k"),
      r1_proj_breakeven_neg100 = colDef(name = "-100k"),
      r1_proj_breakeven_neg75 = colDef(name = "-75k"),
      r1_proj_breakeven_neg50 = colDef(name = "-50k"),
      r1_proj_breakeven_neg25 = colDef(name = "-25k"),
      r1_proj_breakeven_0 = colDef(name = "0k"),
      r1_proj_breakeven_25 = colDef(name = "25k"),
      r1_proj_breakeven_50 = colDef(name = "50k"),
      r1_proj_breakeven_75 = colDef(name = "75k"),
      r1_proj_breakeven_100 = colDef(name = "100k"),
      r1_proj_breakeven_125 = colDef(name = "125k"),
      r1_proj_breakeven_150 = colDef(name = "150k")
    ),
    columnGroups = list(
        colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason")),
        colGroup(name = "R1 score required to acheieve price change of...", columns = c("r1_proj_breakeven_neg150", "r1_proj_breakeven_neg125", "r1_proj_breakeven_neg100", "r1_proj_breakeven_neg75", "r1_proj_breakeven_neg50", "r1_proj_breakeven_neg25", "r1_proj_breakeven_0", "r1_proj_breakeven_25", "r1_proj_breakeven_50", "r1_proj_breakeven_75", "r1_proj_breakeven_100", "r1_proj_breakeven_125", "r1_proj_breakeven_150"))
        ),
    filterable = TRUE,
    defaultPageSize = 10,
    pagination = TRUE
  )
```



# Projected Priced At

Note that below makes an assumption about Magic number decay so is only an estimate.

```{r}

priced_at_table <- r1_projected_price_changes |> 
  arrange(desc(r1_proj_change_priced_at)) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
    priced_at_new = round(price/magic_number_r1, 0),
    across(starts_with("r1_proj_change_"), ~ pmax(round((.x + price)/magic_number_r1, 0), min(priced_at_new)))
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    priced_at_new,
    r1_proj_change_priced_at,
    starts_with("r1_proj_change_")
  ) |> 
  select(
    -r1_proj_change_r0
  )

priced_at_table |> 
  reactable(
    columns = list(
      player_name = colDef(name = "Player", sticky = "left"),
      position = colDef(name = "Position"),
      played_r0 = colDef(name = "Played R0?"),
      starting_price = colDef(name = "Starting Price", format = price_format),
      priced_at_preseason = colDef(name = "Priced At"),
      priced_at_new = colDef(name = "Priced At (Adjusted)*"),
      r1_proj_change_priced_at = colDef(name = "@ Priced At"),
      r1_proj_change_0 = colDef(name = "@ 0"),
      r1_proj_change_10 = colDef(name = "@ 10"),
      r1_proj_change_20 = colDef(name = "@ 20"),
      r1_proj_change_30 = colDef(name = "@ 30"),
      r1_proj_change_40 = colDef(name = "@ 40"),
      r1_proj_change_50 = colDef(name = "@ 50"),
      r1_proj_change_60 = colDef(name = "@ 60"),
      r1_proj_change_70 = colDef(name = "@ 70"),
      r1_proj_change_80 = colDef(name = "@ 80"),
      r1_proj_change_90 = colDef(name = "@ 90"),
      r1_proj_change_100 = colDef(name = "@ 100"),
      r1_proj_change_110 = colDef(name = "@ 110"),
      r1_proj_change_120 = colDef(name = "@ 120"),
      r1_proj_change_130 = colDef(name = "@ 130"),
      r1_proj_change_140 = colDef(name = "@ 140"),
      r1_proj_change_150 = colDef(name = "@ 150")
    ),
    columnGroups = list(
        colGroup(name = "R1 projected 'priced at', if R1 score is ...", columns = c("r1_proj_change_priced_at", "r1_proj_change_0", "r1_proj_change_10", "r1_proj_change_20", "r1_proj_change_30", "r1_proj_change_40", "r1_proj_change_50", "r1_proj_change_60", "r1_proj_change_70", "r1_proj_change_80", "r1_proj_change_90", "r1_proj_change_100", "r1_proj_change_110", "r1_proj_change_120", "r1_proj_change_130", "r1_proj_change_140", "r1_proj_change_150")),
        colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason", "priced_at_new"))
        ),
    filterable = TRUE,
    defaultPageSize = 10,
    pagination = TRUE
  )

```

*: Priced at (adjusted) is adjusted for expected magic number decay.
