---
title: "AFL Fantasy Projected Prices - Round 1"
execute:
  echo: false
  warning: false
---


```{r}

library(arrow)
library(dplyr)
library(reactable)
library(htmltools)
magic_number_r1 <- 10179.88
```

```{r}
r1_projected_price_changes <- read_parquet("https://github.com/bit-in-that/data-automation/raw/main/2026/output/r1_projected_price_changes.parquest")
price_format <- colFormat(separators = TRUE, suffix = "k")
```


# Disclaimer

> The below projections are an *early indication* only, actual price movements may deviate from below due to magic number being different from expected or subtle differences in AFL Fantasy pricing formula from what was applied below.

# R0 Hidden Prices

```{r}
r0_player_table <- r1_projected_price_changes |> 
  filter(
    played_r0
  ) |> 
  transmute(
    player_name,
    position,
    r0_score,
    starting_price = price / 1000,
    price_hidden = price_hidden / 1000,
    price_change_hidden = price_change_hidden / 1000,
    breakeven_hidden,
    r1_proj_change_r0 = r1_proj_change_r0 / 1000,
  ) |> 
  arrange(desc(r0_score))

tagList(
  tags$button(
    "Download CSV",
    onclick = "Reactable.downloadDataCSV('r0-player-hidden', 'bitinthat-r0-player-hidden.csv')"
  ),
  r0_player_table |> 
    reactable(
      columns = list(
      player_name = colDef(name = "Player", sticky = "left"),
      position = colDef(name = "Position"),
      r0_score = colDef(name = "Round 0 Score"),
      starting_price = colDef(name = "Starting Price", format = price_format),
      price_hidden = colDef(name = "Hidden Price", format = price_format),
      price_change_hidden = colDef(name = "Hidden Change", format = price_format),
      breakeven_hidden = colDef(name = "Hidden Breakeven*"),
      r1_proj_change_r0 = colDef(name = "Proj. Price Change @ R0 Score**", format = price_format)
    ),
    filterable = TRUE,
    defaultPageSize = 10,
    pagination = TRUE,
    elementId = "r0-player-hidden"
  )
)


```


*: Breakeven to retain their hidden price
**: Projected price change if they repeat their R0 score


# Projected Price Changes

```{r}

price_change_table <- r1_projected_price_changes |> 
  arrange(desc(r1_proj_change_priced_at)) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
    across(starts_with("r1_proj_change_"), ~ .x/1000)
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    r1_proj_change_priced_at,
    starts_with("r1_proj_change_")
  ) |> 
  select(
    -r1_proj_change_r0
  )

tagList(
  tags$button(
    "Download CSV",
    onclick = "Reactable.downloadDataCSV('r1-projected-price-change', 'bitinthat-r1-projected-price-change.csv')"
  ),
  price_change_table |> 
    reactable(
      columns = list(
        player_name = colDef(name = "Player", sticky = "left"),
        position = colDef(name = "Position"),
        played_r0 = colDef(name = "Played R0?"),
        starting_price = colDef(name = "Starting Price", format = price_format),
        priced_at_preseason = colDef(name = "Priced At"),
        r1_proj_change_priced_at = colDef(name = "@ Priced At", format = price_format),
        r1_proj_change_0 = colDef(name = "@ 0", format = price_format),
        r1_proj_change_10 = colDef(name = "@ 10", format = price_format),
        r1_proj_change_20 = colDef(name = "@ 20", format = price_format),
        r1_proj_change_30 = colDef(name = "@ 30", format = price_format),
        r1_proj_change_40 = colDef(name = "@ 40", format = price_format),
        r1_proj_change_50 = colDef(name = "@ 50", format = price_format),
        r1_proj_change_60 = colDef(name = "@ 60", format = price_format),
        r1_proj_change_70 = colDef(name = "@ 70", format = price_format),
        r1_proj_change_80 = colDef(name = "@ 80", format = price_format),
        r1_proj_change_90 = colDef(name = "@ 90", format = price_format),
        r1_proj_change_100 = colDef(name = "@ 100", format = price_format),
        r1_proj_change_110 = colDef(name = "@ 110", format = price_format),
        r1_proj_change_120 = colDef(name = "@ 120", format = price_format),
        r1_proj_change_130 = colDef(name = "@ 130", format = price_format),
        r1_proj_change_140 = colDef(name = "@ 140", format = price_format),
        r1_proj_change_150 = colDef(name = "@ 150", format = price_format)
      ),
      columnGroups = list(
          colGroup(name = "R1 projected price change, if R1 score is ...", columns = c("r1_proj_change_priced_at", "r1_proj_change_0", "r1_proj_change_10", "r1_proj_change_20", "r1_proj_change_30", "r1_proj_change_40", "r1_proj_change_50", "r1_proj_change_60", "r1_proj_change_70", "r1_proj_change_80", "r1_proj_change_90", "r1_proj_change_100", "r1_proj_change_110", "r1_proj_change_120", "r1_proj_change_130", "r1_proj_change_140", "r1_proj_change_150")),
          colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason"))
          ),
      filterable = TRUE,
      defaultPageSize = 10,
      pagination = TRUE,
      elementId = "r1-projected-price-change"
    )
)
```

# Projected breakeven going into round 2

```{r}

projected_breakeven_table <- r1_projected_price_changes |> 
  arrange(desc(r1_proj_change_priced_at)) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    starts_with("r2_proj_breakeven_")
  )

tagList(
  tags$button(
    "Download CSV",
    onclick = "Reactable.downloadDataCSV('r2-projected-breakeven', 'bitinthat-r2-projected-breakeven.csv')"
  ),
  projected_breakeven_table |> 
    reactable(
      columns = list(
        player_name = colDef(name = "Player", sticky = "left"),
        position = colDef(name = "Position"),
        played_r0 = colDef(name = "Played R0?"),
        starting_price = colDef(name = "Starting Price", format = price_format),
        priced_at_preseason = colDef(name = "Priced At"),
        r2_proj_breakeven_0 = colDef(name = "@ 0"),
        r2_proj_breakeven_10 = colDef(name = "@ 10"),
        r2_proj_breakeven_20 = colDef(name = "@ 20"),
        r2_proj_breakeven_30 = colDef(name = "@ 30"),
        r2_proj_breakeven_40 = colDef(name = "@ 40"),
        r2_proj_breakeven_50 = colDef(name = "@ 50"),
        r2_proj_breakeven_60 = colDef(name = "@ 60"),
        r2_proj_breakeven_70 = colDef(name = "@ 70"),
        r2_proj_breakeven_80 = colDef(name = "@ 80"),
        r2_proj_breakeven_90 = colDef(name = "@ 90"),
        r2_proj_breakeven_100 = colDef(name = "@ 100"),
        r2_proj_breakeven_110 = colDef(name = "@ 110"),
        r2_proj_breakeven_120 = colDef(name = "@ 120"),
        r2_proj_breakeven_130 = colDef(name = "@ 130"),
        r2_proj_breakeven_140 = colDef(name = "@ 140"),
        r2_proj_breakeven_150 = colDef(name = "@ 150")
      ),
      columnGroups = list(
          colGroup(name = "R2 breakeven, if R1 score is ...", columns = c("r2_proj_breakeven_0", "r2_proj_breakeven_10", "r2_proj_breakeven_20", "r2_proj_breakeven_30", "r2_proj_breakeven_40", "r2_proj_breakeven_50", "r2_proj_breakeven_60", "r2_proj_breakeven_70", "r2_proj_breakeven_80", "r2_proj_breakeven_90", "r2_proj_breakeven_100", "r2_proj_breakeven_110", "r2_proj_breakeven_120", "r2_proj_breakeven_130", "r2_proj_breakeven_140", "r2_proj_breakeven_150")),
          colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason"))
          ),
      filterable = TRUE,
      defaultPageSize = 10,
      pagination = TRUE,
      elementId = "r2-projected-breakeven"
    )
)
```


# Score to acheive price change 


```{r}
breakeven_score_table <- r1_projected_price_changes |> 
  arrange(r1_proj_breakeven_0) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    starts_with("r1_proj_breakeven_")
  )

tagList(
  tags$button(
    "Download CSV",
    onclick = "Reactable.downloadDataCSV('r1-score-for-price-change', 'bitinthat-r1-score-for-price-change.csv')"
  ),
  breakeven_score_table |> 
    reactable(
      columns = list(
        player_name = colDef(name = "Player", sticky = "left"),
        position = colDef(name = "Position"),
        played_r0 = colDef(name = "Played R0?"),
        starting_price = colDef(name = "Starting Price", format = price_format),
        priced_at_preseason = colDef(name = "Priced At"),
        r1_proj_breakeven_neg150 = colDef(name = "-150k"),
        r1_proj_breakeven_neg125 = colDef(name = "-125k"),
        r1_proj_breakeven_neg100 = colDef(name = "-100k"),
        r1_proj_breakeven_neg75 = colDef(name = "-75k"),
        r1_proj_breakeven_neg50 = colDef(name = "-50k"),
        r1_proj_breakeven_neg25 = colDef(name = "-25k"),
        r1_proj_breakeven_0 = colDef(name = "0k"),
        r1_proj_breakeven_25 = colDef(name = "25k"),
        r1_proj_breakeven_50 = colDef(name = "50k"),
        r1_proj_breakeven_75 = colDef(name = "75k"),
        r1_proj_breakeven_100 = colDef(name = "100k"),
        r1_proj_breakeven_125 = colDef(name = "125k"),
        r1_proj_breakeven_150 = colDef(name = "150k")
      ),
      columnGroups = list(
          colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason")),
          colGroup(name = "R1 score required to acheieve price change of...", columns = c("r1_proj_breakeven_neg150", "r1_proj_breakeven_neg125", "r1_proj_breakeven_neg100", "r1_proj_breakeven_neg75", "r1_proj_breakeven_neg50", "r1_proj_breakeven_neg25", "r1_proj_breakeven_0", "r1_proj_breakeven_25", "r1_proj_breakeven_50", "r1_proj_breakeven_75", "r1_proj_breakeven_100", "r1_proj_breakeven_125", "r1_proj_breakeven_150"))
          ),
      filterable = TRUE,
      defaultPageSize = 10,
      pagination = TRUE,
      elementId = "r1-score-for-price-change"
    )
)
```



# Projected Priced At

Note that below makes an assumption about Magic number decay so is only an estimate.

```{r}

priced_at_table <- r1_projected_price_changes |> 
  arrange(desc(r1_proj_change_priced_at)) |> 
  mutate(
    played_r0 = if_else(played_r0, "Yes", "No"),
    starting_price = price / 1000,
    priced_at_new = round(price/magic_number_r1, 0),
    across(starts_with("r1_proj_change_"), ~ pmax(round((.x + price)/magic_number_r1, 0), min(priced_at_new)))
  ) |> 
  select(
    player_name,
    position,
    played_r0,
    starting_price,
    priced_at_preseason,
    priced_at_new,
    r1_proj_change_priced_at,
    starts_with("r1_proj_change_")
  ) |> 
  select(
    -r1_proj_change_r0
  )

tagList(
  tags$button(
    "Download CSV",
    onclick = "Reactable.downloadDataCSV('r1-projected-priced-at', 'bitinthat-r1-projected-priced-at.csv')"
  ),
  priced_at_table |> 
    reactable(
      columns = list(
        player_name = colDef(name = "Player", sticky = "left"),
        position = colDef(name = "Position"),
        played_r0 = colDef(name = "Played R0?"),
        starting_price = colDef(name = "Starting Price", format = price_format),
        priced_at_preseason = colDef(name = "Priced At"),
        priced_at_new = colDef(name = "Priced At (Adjusted)*"),
        r1_proj_change_priced_at = colDef(name = "@ Priced At"),
        r1_proj_change_0 = colDef(name = "@ 0"),
        r1_proj_change_10 = colDef(name = "@ 10"),
        r1_proj_change_20 = colDef(name = "@ 20"),
        r1_proj_change_30 = colDef(name = "@ 30"),
        r1_proj_change_40 = colDef(name = "@ 40"),
        r1_proj_change_50 = colDef(name = "@ 50"),
        r1_proj_change_60 = colDef(name = "@ 60"),
        r1_proj_change_70 = colDef(name = "@ 70"),
        r1_proj_change_80 = colDef(name = "@ 80"),
        r1_proj_change_90 = colDef(name = "@ 90"),
        r1_proj_change_100 = colDef(name = "@ 100"),
        r1_proj_change_110 = colDef(name = "@ 110"),
        r1_proj_change_120 = colDef(name = "@ 120"),
        r1_proj_change_130 = colDef(name = "@ 130"),
        r1_proj_change_140 = colDef(name = "@ 140"),
        r1_proj_change_150 = colDef(name = "@ 150")
      ),
      columnGroups = list(
          colGroup(name = "R1 projected 'priced at', if R1 score is ...", columns = c("r1_proj_change_priced_at", "r1_proj_change_0", "r1_proj_change_10", "r1_proj_change_20", "r1_proj_change_30", "r1_proj_change_40", "r1_proj_change_50", "r1_proj_change_60", "r1_proj_change_70", "r1_proj_change_80", "r1_proj_change_90", "r1_proj_change_100", "r1_proj_change_110", "r1_proj_change_120", "r1_proj_change_130", "r1_proj_change_140", "r1_proj_change_150")),
          colGroup(name = "Player info", columns = c("position", "played_r0", "starting_price", "priced_at_preseason", "priced_at_new"))
          ),
      filterable = TRUE,
      defaultPageSize = 10,
      pagination = TRUE,
      elementId = "r1-projected-priced-at"
    )
)
```

*: Priced at (adjusted) is adjusted for expected magic number decay.
